Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-09-10 manuscript.tex
Accepted for publication [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/0e2445c24e13ea304a7439efa969e7a0fc2309cd.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/0e2445c24e13ea304a7439efa969e7a0fc2309cd/checks
https://github.com/habi/acinar-analysis-manuscript/runs/1220547950

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...4f0f379e0927ddbc18d27f425c700afd12fc7e42}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/4f0f379e0927ddbc18d27f425c700afd12fc7e42/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/4f0f379e0927ddbc18d27f425c700afd12fc7e42}{habi/acinar-analysis-manuscript@4f0f379}
on September 9, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(4f0f379)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(4f0f379)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

All the stereologically assessed data was processed in a \href{http://jupyter.org/}{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{37}{]} notebook, producing all the results, including the statistical data and plots shown below.
The notebook with all its history is freely available on GitHub {[}\protect\hyperlink{ref-V87xbt0b}{38}{]}.
The performed calculations are described in detail in the \protect\hyperlink{results}{Results} section.
In the plots, semitransparent circles mark the single observations.
The box shows the 25~\%--75~\% quartiles range of the data.
The whiskers extend to the rest of the distribution.
Outliers are determined as a function of the inter-quartile range and are shown outside the whiskers.
Numerical values in the text are given as averages ± standard deviation.
P-values in the text and figure legends are given as precise numbers, as suggested by Amhrein et al.~{[}\protect\hyperlink{ref-o21zxPIu}{39}{]}.

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-TsNwin2E}{}%
1. Schittny JC, Burri PH. Development and growth of the lung. 4th Editio. In: Fishman A, Elias J, Fishman J, Grippi M, Senior R, Pack A, editors. Fishman's pulmonary diseases and disorders. 4th Editio. McGraw-Hill Professional; 2008. pp. 91--114. Available: \url{http://amazon.com/o/ASIN/0071457399/}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been accepted for publication in \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...0e2445c24e13ea304a7439efa969e7a0fc2309cd}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/0e2445c24e13ea304a7439efa969e7a0fc2309cd/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/0e2445c24e13ea304a7439efa969e7a0fc2309cd}{habi/acinar-analysis-manuscript@0e2445c}
on September 10, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(0e2445c)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(0e2445c)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

All the stereologically assessed data was processed in a \href{http://jupyter.org/}{Jupyter} {[}\protect\hyperlink{ref-pQ6Wbz73}{37}{]} notebook, producing all the results, including the statistical data and plots shown below.
The notebook with all its history is freely available on GitHub {[}\protect\hyperlink{ref-V87xbt0b}{38}{]}.
The performed calculations are described in detail in the \protect\hyperlink{results}{Results} section.
In the plots, semitransparent circles mark the single observations.
The box shows the 25~\%--75~\% quartiles range of the data.
The whiskers extend to the rest of the distribution.
Outliers are determined as a function of the inter-quartile range and are shown outside the whiskers.
Numerical values in the text are given as averages ± standard deviation.
P-values in the text and figure legends are given as precise numbers, as suggested by Amrhein et al.~{[}\protect\hyperlink{ref-o21zxPIu}{39}{]}.

@@

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-TsNwin2E}{}%
1. Schittny JC, Burri PH. Development and growth of the lung. 4th Edition. In: Fishman A, Elias J, Fishman J, Grippi M, Senior R, Pack A, editors. Fishman's pulmonary diseases and disorders. 4th Edition. McGraw-Hill Professional; 2008. pp. 91--114. Available: \url{http://amazon.com/o/ASIN/0071457399/}
